Sampling Strategies in Decisions from Experience

### 2022-04-26 manuscript.Rmd
Update Discussion

---
title             : |
  Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation

@@

To substantiate the discussion, the model is used to simulate the sampling and accumulation process for choices between a safe and a two-outcome prospect, while systematically combining different switching probabilities and thresholds.
Considering choice rates and parameter estimates of cumulative prospect theory [@tverskyAdvancesProspectTheory1992], the computational analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
Importantly, the analysis also shows that these distinct choice patterns become more robust with increasing thresholds.
Before presenting the model and the computational analysis, the following section provides a formal definition of prospects.

# Formal Definition of Prospects

@@

### Formal Review of CPT

@@

[...]

>>>>

---
title             : |
  Sampling Strategies in Decisions from Experience

@@

To substantiate the discussion, the model is used to simulate the sampling and accumulation process for choices between a safe and a two-outcome prospect, while systematically combining different switching probabilities and thresholds.
Considering choice rates and parameter estimates of cumulative prospect theory [@tverskyAdvancesProspectTheory1992], the computational analysis shows that the choices converge to the solutions of EV maximization for low switching probabilities, but take the form of an as-if underweighting of rare outcomes for high switching probabilities.
Importantly, the analysis also shows that these distinct choice patterns become more robust with increasing thresholds.
Before presenting the model and the computational analysis, the following section provides a definition of prospects.

# Definition of Prospects

@@

### Desription of CPT

@@

The predictions of the choice patterns and CPT parameters alone do not render the model theoretically or empirically meaningful. 
It is right that cognitive models are underdetermined by "locally obtained" data and that they should not aim to merely explain effects---e.g., the as-if underweighting of rare outcomes---but fundamental capacities such as learning, reasoning, and decision making [@vanrooijTheoryTestHow2021].
In explaining these capacities, cognitive models must be constrained to the extent that neither the computational resources of the human mind nor other relevant resources---e.g., time---are limitless [see, e.g., @jareckiFrameworkBuildingCognitive2020; @liederResourcerationalAnalysisUnderstanding2020; @vanrooijTheoryTestHow2021].
Acknowledging these limitations, different theoretical frameworks can be used to narrow down the still abundant number of possible mechanisms the mind might employ in the decision-making process.
Such frameworks build on different, sometimes related or complementary assumptions, e.g.: *ecological rationality* holds that the mind uses simple (decision) heuristics that exploit the information structures of the environment in which it operates [see, e.g., @payneAdaptiveStrategySelection1988; see also @simonRationalChoiceStructure1956]; sequential sampling models assume that the mind trades of processing speed and accuracy while accumulating evidence for or against choice alternatives [see, e.g., @ratcliffComparisonSequentialSampling2004; @bogaczPhysicsOptimalDecision2006]; and *resource rationality* assumes that the mind employs mechanisms that make optimal use of its actual resources in obtaining a specific goal [see, e.g.; @liederResourcerationalAnalysisUnderstanding2020].

Admittingly, although the current paper ought to sketch how the mind might exercise the capacity of making decisions from experience, it dealt with these constraints and frameworks rather implicitly and loosely.

<!-- Marr: What is the goal and how can it be achieved -->

<!-- Using CPT as effects -->

# Conclusion
